animbook: An R Package for Visualize \ldots{}

### 2023-09-05 animbook-journal.tex
add new section

The structure of this paper will consist of four main section. The first section is domain problem and data characterization, identifying the problems the visualization tools try to solve. Secondly, the operation and data type abstraction, the description of operations, and the types of data required for the next stage. The third section is visualization and interaction design, designing the visuals and refining the tools. In the last section, package design, develop the structure of the packages and how to implement the final visualize design into the R package. The checking of the threat and validating of that threat will be carried out throughout the entire process of designing the animbook package.

\hypertarget{domain-problem-and-data-characterization}{%
\section{Domain problem and data characterization}\label{domain-problem-and-data-characterization}}

@@

>>>>

The structure of this paper will consist of four main section. The first section is domain problem and data characterization, identifying the problems the visualization tools try to solve. Secondly, the operation and data type abstraction, the description of operations, and the types of data required for the next stage. The third section is visualization and interaction design, designing the visuals and refining the tools. In the forth section, package design, develop the structure of the packages and how to implement the final visualize design into the R package. Lastly, the package usage. The checking of the threat and validating of that threat will be carried out throughout the entire process of designing the animbook package.

\hypertarget{problem-and-data-characterization}{%
\section{Problem and data characterization}\label{problem-and-data-characterization}}

@@

\hypertarget{package-usage}{%
\section{Package Usage}\label{package-usage}}
